Efficient Coalition Formation \\ for Web Services

### 2013-05-11 papers/coalition-journal-extension/coalition_journal.tex
Changes

{\bf Definition 2 (Core)} A payoff vector $x$ is in the $core$ of
a coalitional game $(N, v)$ if and only if:
\begin{equation}\label{eq:core3}
\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)
\end{equation}

@@

\newtheorem{theorem}{Proposition}
%\begin{theorem}[Einstein-Podolsky-Rosenberg]
\begin{theorem}
A game with a characteristic function $v$
is convex if and only if for all $S$, $T$, and $i$ where $S
\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
N$,
%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
\begin{equation}\label{eq:convex_snow}
v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
\end{equation}
\end{theorem}

@@

Our algorithm works as follows. We have an established community
with a master and some member web services already residing in the
community. A web service would send a join request to the
community. The ideal solution would be analyzing the \emph{core}
or \emph{$\epsilon$-core} stability of the group having this new
member. As the normal core membership algorithm is computationally
intractable, we exploit Proposition \ref{proposition} and Equation
\ref{eq:convex_snow} to check the convexity of our game having
characteristic function where the new member is added. In the
equation, we set $C$ to be our community members $(C)$ before
having the new web service. We assign ${i}$ to the new web
service, and then verify the equation for $S$, setting $ S = T /
W1 $ where $W1$ is the set of all possible subsets of the set $N$
having the size $1$. We can relax the equation a bit by adding a
constant $\epsilon$ to the left side of the equation. We call this
method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
satisfied for all $W1$, we let the new web service join our
community, since the web service will contribute positively enough
to make our new community stable. Since only subsets of size $1$
are checked, the following Proposition holds.

\begin{Proposition}\label{complexity1}
The run time complexity of Depth-1 Convex-Checker algorithm is
$O(n)$.
\end{Proposition}

@@

\begin{Proposition}\label{complexity2}
The run time complexity of Depth-2 Convex-Checker algorithm is
$O(n^2)$.
\end{Proposition}

>>>>

{\bf Definition 2 (Core)} A payoff vector $x$ is in the $core$ of
a coalitional game $(N, v)$ if and only if:
\begin{equation}\label{eq:core}
\forall S \subseteq N, \sum_{x_i \in S} x_i \geq v(S)
\end{equation}

@@

\newtheorem{theorem}{Proposition}
%\begin{theorem}[Einstein-Podolsky-Rosenberg]
\begin{theorem}\label{proposition1}
A game with a characteristic function $v$
is convex if and only if for all $S$, $T$, and $i$ where $S
\subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in
N$,
%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
\begin{equation}\label{eq:convex_snow}
v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
\end{equation}
\end{theorem}

@@

Our algorithm works as follows. We have an established community
with a master and some member web services already residing in the
community. A web service would send a join request to the
community. The ideal solution would be analyzing the \emph{core}
or \emph{$\epsilon$-core} stability of the group having this new
member. As the normal core membership algorithm is computationally
intractable, we exploit Proposition \ref{proposition1} and Equation
\ref{eq:convex_snow} to check the convexity of our game having
characteristic function where the new member is added. In the
equation, we set $C$ to be our community members $(C)$ before
having the new web service. We assign ${i}$ to the new web
service, and then verify the equation for $S$, setting $ S = T /
W1 $ where $W1$ is the set of all possible subsets of the set $N$
having the size $1$. We can relax the equation a bit by adding a
constant $\epsilon$ to the left side of the equation. We call this
method \emph{Depth-1 Convex-Checker} algorithm. If the equation is
satisfied for all $W1$, we let the new web service join our
community, since the web service will contribute positively enough
to make our new community stable. Since only subsets of size $1$
are checked, the following Proposition holds.

\begin{theorem}\label{complexity1}
\emph{The run time complexity of Depth-1 Convex-Checker algorithm is
$O(n)$.}
\end{theorem}

@@

\begin{theorem}\label{complexity2}
\emph{The run time complexity of Depth-2 Convex-Checker algorithm is
$O(n^2)$.}
\end{theorem}
